### 2018-12-29 Sections/intro_to_QM.tex
Schroedinger vs Heisenberg pictures

\section{Introduction to quantum mechanics}

@@

>>>>

\section{Introduction to quantum mechanics}\index{Quantum mechanics}\label{sec:intro_to_QM}

@@

% Schroedinger vs Heisenberg pictures

\subsubsection{Schr{\" o}dinger vs Heisenberg pictures}

The above formalism describes quantum evolution by acting the unitary operator on the quantum state directly,
\begin{align}
\ket{\psi'} = \hat{U}\ket\psi.
\end{align}
This is known as the \textit{Schr{\" o}dinger picture}\index{Schr{\" o}dinger picture}. An alternate, but entirely mathematically equivalent approach is the \textit{Heisenberg picture}\index{Heisenberg picture}, whereby we evolve the operators acting upon a state, rather than the state itself. Now the operator evolution is described by conjugating the operators with the unitary operator describing the evolution. That is, representing the quantum state in terms of some operator $\hat{o}$, the operator evolution proceeds as,
\begin{align}
	\hat{o}' = \hat{U}\hat{o}\hat{U}^\dag.
\end{align}

For example, representing photonic states using creation operators $\hat{a}^\dag$ (introduced in Sec.~\ref{sec:creation_ann_ops}), the evolved creation operator is simply given by $\hat{U}\hat{a}^\dag\hat{U}^\dag$. In quantum optics in particular, where creation operator representations are highly convenient, this is a very useful formulation for describing quantum evolution.
